Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning

### 2024-10-02 paper-2024-sac-marl-neighbouring-strategies.tex
start to put citations

\section{Introduction}
The increasing complexity of real-world systems, from robotic swarms to smart grids, demands intelligent control strategies capable of adapting to dynamic and often unpredictable environments.
%
In this direction, reinforcement learning (RL)~\cite{sutton2018reinforcement} has emerged as a powerful paradigm for training agents to interact with their environment and learn optimal policies through trial and error.
%
Moving beyond single-agent settings, multi-agent reinforcement learning (MARL)~\cite{bucsoniu2010multi} extends RL to scenarios where multiple agents must collaborate or compete to achieve a common goal.
%
Recent advances in deep learning have further revolutionized the field, 
enabling the training of complex policies in high-dimensional state and action spaces, 
leading to the emergence of multi-agent deep reinforcement learning (MADRL)~\cite{gronauer2022multi}.
%
MADRL has gained significant traction due to its flexibility and capacity to learn diverse behaviors, 
ranging from cooperative~\cite{gupta2017cooperative} to competitive~\cite{tampuu2017multiagent}, 
as demonstrated in various case studies involving video games~\cite{shao2019survey}, robotics~\cite{orr2023multi},
and traffic management. 
%
This paper focuses on the subdomain of cooperative multi-agent reinforcement learning, 
a particularly active and impactful area of research within MADRL.

Many prominent approaches in this field employ a centralized training and decentralized execution paradigm
 (e.g., COMA, MAPPO, MADPG), 
 where a centralized learner trains distributed policies that are subsequently executed independently. 
 While facilitating decentralized runtime operation and avoiding single points of failure, 
 this approach typically entails an offline learning phase (using simulators and centralized computation) 
 followed by online execution with no further learning. 
 This inherent limitation hinders adaptation to changing environments or tasks at runtime.  
 While fully independent learners offer a potential solution for online learning,
 they often underperform centralized counterparts due to instability in training and a lack of differentiation between agents and their interactions with the environment. 
 %
 However, in many real-world multi-agent systems, 
 agents only interact with a limited subset of the overall system, 
 as exemplified by limited sensing ranges in swarm robotics or localized interactions.  
 This observation also holds true in other natural systems, such as animal herds.

>>>>

\section{Introduction}
The increasing complexity of real-world systems, from robotic swarms to smart grids, demands intelligent control strategies capable of adapting to dynamic and often unpredictable environments.
%
In this direction, reinforcement learning (RL)~\cite{sutton2018reinforcement} has emerged as a powerful paradigm for training agents to interact with their environment and learn optimal policies through trial and error.
%
Moving beyond single-agent settings, multi-agent reinforcement learning (MARL)~\cite{bucsoniu2010multi} extends RL to scenarios where multiple agents must collaborate or compete to achieve a common goal.
%
Recent advances in deep learning have further revolutionized the field, 
enabling the training of complex policies in high-dimensional state and action spaces, 
leading to the emergence of multi-agent deep reinforcement learning (MADRL)~\cite{gronauer2022multi}.
%
MADRL has gained significant traction due to its flexibility and capacity to learn diverse behaviors, 
ranging from cooperative~\cite{gupta2017cooperative} to competitive~\cite{tampuu2017multiagent}, 
as demonstrated in various case studies involving video games~\cite{shao2019survey}, robotics~\cite{orr2023multi},
and traffic management. 
%
This paper focuses on the subdomain of cooperative multi-agent reinforcement learning, 
a particularly active and impactful area of research within MADRL~\cite{oroojlooy2023review}.

\sloppy
Many prominent approaches in this field employ a centralized training and decentralized execution paradigm
 (e.g., COMA~\cite{foerster2018counterfactual}, MAPPO~\cite{yu2022surprising}, MADPG), 
 where a centralized learner trains distributed policies that are subsequently executed independently. 
 While facilitating decentralized runtime operation and avoiding single points of failure, 
 this approach typically entails an offline learning phase (using simulators and centralized computation) 
 followed by online execution with no further learning. 
 This inherent limitation hinders adaptation to changing environments or tasks at runtime.  
 While fully independent learners offer a potential solution for online learning,
 they often underperform centralized counterparts due to instability in training and a lack of differentiation between agents and their interactions with the environment. 
 %
 However, in many real-world multi-agent systems, 
 agents only interact with a limited subset of the overall system, 
 as exemplified by limited sensing ranges in swarm robotics or localized interactions.  
 This observation also holds true in other natural systems, such as animal herds.
